Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-10-15 ms.tex
more on CV3.

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
\caption{Weak Lans +8 PSF during CV3 testing.
The central peak is used for centroiding the 70 pixel radius circular aperture.}\label{fig:WLP8PSF}
\end{figure}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{plot_mmm.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign.
The WLP8SUB (subarray) showed the smallest standard deviation of any NIRCam mode explored.}\label{fig:CV3longTser}
\end{figure}

>>>>

During the Cyrogenic Vacuum Test 3, the Integrated Science Instrument Module (ISIM) was placed in a vacuum chamber with a simulated telescope to illuminate the detectors in a similar way as during flight with an instrument called the Optical telescope element simulator (OSIM).
Of all ground-based tests discussed in this work, the point spread function most closely resembled the JWST flight point spread function.

CV3 included a series of exposures over nearly 24 hours with an LED lamp in imaging mode to test the fundamental photometric performance.
The LED was a narrowband source at 1.55 $\mu$m, which was used in imaging mode since this would result in a narrow-lined spectrum.
While the spectroscopic modes are expected to be the most scientifically interesting modes for studying exoplanet atmospheres, the broadband lamps needed to produce a spectrum tend to be less stable than LEDs.
Therefore, the test was designed with an LED with the hope of measuring the precision possible with the NIRCam optics and detector.

As with the spatial scanning mode on HST \citep[e.g.][]{}, spreading the light of a source over many pixels can improve the precision

NIRCam instrument was 
 package (was lowered into

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{wlp8_psf.pdf}
\caption{Weak Lans +8 PSF during CV3 testing.
The central peak is used for centroiding, while the entire PSF is used for aperture photometry.
A 70 pixel radius aperture (shown here is a black circle) is used for the source aperture.}\label{fig:WLP8PSF}
\end{figure}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{plot_mmm.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign.
All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
13 tests (FULL1 through FULLQ) are all in full frame mode, while WLP8SUB used a 320$\times$320 subarray and WLP8SUB640 used a 640$\times$640 subarray.
The WLP8SUB showed the smallest standard deviation of any testof any NIRCam mode explored.}\label{fig:CV3longTser}
\end{figure}
